---
title: "Project"
output: html_document
date: "2024-06-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2.1 Title

The title of the report and the name of the student.
Hajara Eve Muzammal
An Investigation of Body Fat and Anthropometric Measurements in Females 25–30 Years of Age


### 2.4 Description of data

Need give to do the descriptive statistics analysis of the data set. For example, using the summary to describe the factor variable or using a bar plot, a hist plot to describe the numerical variable, or using a scatter plot to describe the relation between two variables.

```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Create the data frame
data <- data.frame(
  y = c(19.5, 24.7, 30.7, 29.8, 19.1, 25.6, 31.4, 27.9, 22.1, 25.5, 31.1, 30.4, 18.7, 19.7, 14.6, 29.5, 27.7, 30.2, 22.7, 25.2),
  x1 = c(43.1, 49.8, 51.9, 54.3, 42.2, 53.9, 58.5, 52.1, 49.9, 53.5, 56.6, 56.7, 46.5, 44.2, 42.7, 54.4, 55.3, 58.6, 48.2, 51.0),
  x2 = c(29.1, 28.2, 37.0, 31.1, 30.9, 23.7, 27.6, 30.6, 23.2, 24.8, 30.0, 28.3, 23.0, 28.6, 21.3, 30.1, 25.7, 24.6, 27.1, 27.5),
  x3 = c(11.9, 22.8, 18.7, 20.1, 12.9, 21.7, 27.1, 25.4, 21.3, 19.3, 25.4, 27.2, 11.7, 17.8, 12.8, 23.9, 22.6, 25.4, 14.8, 21.1)
)

# Summary of the data
summary(data)
# Scatter plot of body fat percentage vs. triceps skinfold thickness
ggplot(data, aes(x = x1, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Body Fat Percentage vs. Triceps Skinfold Thickness", x = "Triceps Skinfold Thickness", y = "Body Fat Percentage")

# Scatter plot of body fat percentage vs. thigh circumference
ggplot(data, aes(x = x2, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Body Fat Percentage vs. Thigh Circumference", x = "Thigh Circumference", y = "Body Fat Percentage")

# Scatter plot of body fat percentage vs. midarm circumference
ggplot(data, aes(x = x3, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "Body Fat Percentage vs. Midarm Circumference", x = "Midarm Circumference", y = "Body Fat Percentage")

```

### 2.5 Methods and Results

```{r}
# Fit the linear model
model <- lm(y ~ x1 + x2 + x3, data = data)

# Summary of the model
summary(model)

# Residual diagnostics
par(mfrow = c(2, 2))
plot(model)

```



## 3 Data Set


2. http://calcnet.mth.cmich.edu/org/spss/prj_body_fat_data.htm
